Quantum Interval-Valued Probability: Contextuality and the Born Rule

### 2017-10-20 prop_letter.tex
prop_letter.tex \section{Born rule and Gleason's Theorem} Updating...

\section{Gleason's Theorem and Born rule}

@@

\noindent Because Eqs.~(\ref{eq:iota-constraints}) are the direct
counterpart of Eqs.~(\ref{eq:QIVPM-constraints}) and Eq.~(\ref{eq:iota-Inclusion})
is the direct counterpart of the convexity condition, Eq.~(\ref{eq:classicalconvex})
and Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}),
$\iota\circ\mu$ should always be a IVPM no matter in classical or
quantum case. Conversely, if $\iota\circ\mu$ is always a IVPM, then
$\iota$ must be a THOS rule. In other words, $\iota$ is a THOS rule
is a necessary and sufficient condition for $\iota\circ\mu$ is always
a IVPM as we next show.

@@

As we have discussed, Statement~\ref{enu:iota-subject-to} implies
\ref{enu:iota-mu-QIVPM}. The rest of the proof is to prove that if
$\iota$ is not a THOS rule, then $\iota\circ\mu$ might not be a
QIVPM. If $\iota$ doesn't satisfy Eq.~(\ref{eq:iota-Inclusion}),
we can find three particular numbers~$x_{0}$, $x_{1}$, and $x_{2}\in\left[0,1\right]$
such that $x_{0}+x_{1}+x_{2}\in\left[0,1\right]$, but $\iota\left(x_{0}+x_{1}+x_{2}\right)+\iota\left(x_{2}\right)\nsubseteq\iota\left(x_{0}+x_{2}\right)+\iota\left(x_{1}+x_{2}\right)$.
Consider the state $\rho=x_{0}\proj{0}+x_{1}\proj{1}+x_{2}\proj{2}+\left(1-x_{0}-x_{1}-x_{2}\right)\proj{3}$.
Then, the function~$\iota\circ\mu_{\rho}^{\mathrm{\mathrm{B}}}$
fails to satisfy Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion})
\begin{eqnarray*}
 &  & \iota\left(\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(\proj{0}+\proj{1}+\proj{2}\right)\right)+\iota\left(\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(\proj{2}\right)\right)\\
 & \nsubseteq & \iota\left(\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(\proj{0}+\proj{2}\right)\right)+\iota\left(\mu_{\rho}^{\mathrm{\mathrm{B}}}\left(\proj{1}+\proj{2}\right)\right)\,,
\end{eqnarray*}
and cannot be a QIVPM. Therefore, $\iota$ is a THOS rule if and only
if $\iota\circ\mu$ is always a QIVPM. Similarly, Statement~\ref{enu:iota-subject-to}
and \ref{enu:iota-mu-CIVPM} are equivalent as well~\citep{HOSTunpublished}.

>>>>

\section{Born rule and Gleason's Theorem}

@@

\noindent The first three constraints, Eqs.~(\ref{eq:iota-constraints}),
are the direct counterpart of the corresponding QIVPM constraints,
Eqs.~(\ref{eq:QIVPM-constraints}); the last condition, Eq.~(\ref{eq:iota-Inclusion}),
is the direct counterpart of the convexity condition, Eq.~(\ref{eq:classicalconvex})
and (\ref{eq:QuantumInterval-valuedProbability-Inclusion}). Therefore
the composited function~$\iota\circ\mu$ satisfies the constraints
for IVPMs naturally no matter in classical or quantum case. Conversely,
if $\iota\circ\mu$ is always a IVPM, then $\iota$ must be a THOS
rule. In other words, $\iota$ is a THOS rule is a necessary and sufficient
condition for $\iota\circ\mu$ is always a IVPM as we next show.

@@

As we have discussed, Statement~\ref{enu:iota-subject-to} implies
\ref{enu:iota-mu-QIVPM}. The rest of the proof is to show that if
$\iota$ is not a THOS rule, then $\iota\circ\mu$ might not be a
QIVPM. Suppose there are three particular numbers~$x_{0}$, $x_{1}$,
and $x_{2}\in\left[0,1\right]$ such that $x_{0}+x_{1}+x_{2}\in\left[0,1\right]$,
but they doesn't satisfy Eq.~(\ref{eq:iota-Inclusion}). Consider
the state 
\begin{equation}
\begin{aligned}\rho={} & x_{0}\proj{0}+x_{1}\proj{1}+x_{2}\proj{2}\\
 & +\left(1-x_{0}-x_{1}-x_{2}\right)\proj{3}\,.
\end{aligned}
\end{equation}
When $P_{0}=\proj{0}+\proj{2}$ and $P_{1}=\proj{1}+\proj{2}$, we
have $P_{0}P_{1}=\proj{2}$ and $P_{0}+P_{1}-P_{0}P_{1}=\proj{0}+\proj{1}+\proj{2}$.
By applying $\iota\circ\mu_{\rho}^{\mathrm{\mathrm{B}}}$ on these
projectors, Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion})
becomes Eq.~(\ref{eq:iota-Inclusion}) which cannot be satisfied
by how we pick $x_{0}$, $x_{1}$, and $x_{2}$. Therefore, $\iota$
is a THOS rule if and only if $\iota\circ\mu$ is always a QIVPM.
Similarly, Statement~\ref{enu:iota-subject-to} and \ref{enu:iota-mu-CIVPM}
are equivalent as well~\citep{HOSTunpublished}.
